---
title: "USBondAnalysis"
author: "Shubham Misar"
date: "2023-06-17"
output: html_document
---

```{r}
library(tsibble)
library(dplyr)
library(ggplot2)
library(fabletools)
library(feasts)
library(tsibbledata)
library(forecast)
library(tidyverse)


```

## Data Preprocessing

```{r}
df <- read.csv("FED-SVENY.csv")
```

```{r}
head(df)
```

Lets Convert the Date column into datetime format and make it into index

```{r}
df<-df %>% 
  mutate(Date = as.Date(Date)) %>% 
  as_tsibble(index = Date)
```

```{r}
head(df)
```

## EDA

```{r}
df %>% 
  autoplot(SVENY01) +
  labs(
    x = "Date",
    y = "Returns",
    title = "1 Year Bond Returns"
  )
```

For the 1980s the returns were the highest, which declined over time till 2020 and then picked up again.


```{r}
df_long <- df %>%
  pivot_longer(cols = -Date, names_to = "Variable", values_to = "Value")
```


```{r, warning=FALSE}
library(ggplot2)
library(ggthemes)

df_long %>%
  ggplot(aes(x = Date, y = Value, color = Variable)) +
  geom_line(linetype = "solid", size = 1.5) +  
  scale_color_viridis_d() +  
  labs(
    x = "Date",
    y = "Bond Yield in %",
    title = "Bond Yield Comparison"
  ) +
  theme_minimal() +  
  theme(
    plot.title = element_text(size = 16, face = "bold"),  
    axis.title = element_text(size = 14),  
    axis.text = element_text(size = 12),  
    legend.title = element_blank(),  
    legend.position = "bottom"  
  )

```

As the term for investment increases the returns are higher.

During the 1980s The investment percentage was the highest.

Lets choose SVENY01, SVENY07 and SVENY20 to forecast 



The dataset we have missing dates lets backfill the data and the missing dates to decompose the data.

```{r}
date_range <- data.frame(Date = seq(min(df$Date), max(df$Date), by = "day"))
df_filled <- date_range %>%
  left_join(df, by = "Date") %>%
  fill(everything(), .direction = "down") %>% 
  as_tsibble(index = Date)

```


```{r}
dcap <- df_filled %>%
  model(classical_decomposition = classical_decomposition(SVENY01, type  = 'additive'))
```


```{r}

date_range <- data.frame(Date = seq(min(df$Date), max(df$Date), by = "day"))


df_filled <- date_range %>%
  left_join(df, by = "Date") %>%
  fill(everything(), .direction = "down") %>% 
  as_tsibble(index = Date)


head(df_filled)
```

```{r, fig.height=8}
df_filled %>%
  gg_season(SVENY01, labels = "right") +
  labs(
    title = "Seasonal Pattern of SVENY01",
    x = "Season",
    y = NULL,
    fill = "Year"
  ) +
  theme_minimal() +
  theme(
    legend.position = "top"
  ) +
  guides(color = guide_legend(override.aes = list(size = 1))) +
  guides(fill = guide_legend(override.aes = list(size = 1))) +
  theme(legend.key.size = unit(1, "lines"))



```


The above plot we see around 1970s and 1980s there were high returns, no particular seasonlity 

### Decomposition

### SVENY01

```{r}
dcamp <- df_filled %>%
  model(classical_decomposition = classical_decomposition(SVENY01, type = 'additive')) 
```

```{r, warning=FALSE}
components(dcamp) %>% 
  autoplot()
```

There is no seasonality we see but we see high variance around 1980s.


### SVENY07


```{r}
dcamp <- df_filled %>%
  model(classical_decomposition = classical_decomposition(SVENY07, type = 'additive')) 
```

```{r, warning=FALSE}
components(dcamp) %>% 
  autoplot()
```
More variance than SVENYO1, also more on the positive side


### SVENY20

```{r}
dcamp <- df_filled %>%
  model(classical_decomposition = classical_decomposition(SVENY20, type = 'additive')) 
```

```{r, warning=FALSE}
components(dcamp) %>% 
  autoplot()
```

The data is shifting since 2020 lets looks closer.


```{r}
df %>%
  filter( "2020-08-01" > Date & Date > "2019-05-01" ) %>%
  ggplot() +
  geom_line(aes(x = Date, y = SVENY01, color = "SVENY01"), linetype = "solid", size = 0.8) +
  geom_line(aes(x = Date, y = SVENY20, color = "SVENY20"), linetype = "solid", size = 0.8) +
  geom_line(aes(x = Date, y = SVENY07, color = "SVENY07"), linetype = "solid", size = 0.8) +
  geom_line(aes(x = Date, y = SVENY30, color = "SVENY30"), linetype = "solid", size = 0.8) +
  labs(
    x = "Date",
    y = "Bond Yield",
    title = "Bond Yield Comparison Just Before COVID",
    color = "Series",
    linetype = "Series"
  ) +
  scale_color_manual(
    values = c("#0072B2", "#D55E00", "#009E73", "#CC79A7"),
    labels = c("SVENY01", "SVENY20", "SVENY07", "SVENY30")
  ) +
  scale_linetype_manual(
    values = c("solid", "solid", "solid", "solid"),
    labels = c("SVENY01", "SVENY20", "SVENY07", "SVENY30")
  ) +
  theme_minimal() +
  guides(
    color = guide_legend(override.aes = list(linetype = "solid")),
    linetype = guide_legend()
  )


```

Bond values decreased from March 2020 specifically for SVENY01 went down far down.

```{r}
df %>%
  filter(Date > "2022-05-01") %>%
  ggplot() +
  geom_line(aes(x = Date, y = SVENY01, color = "SVENY01"), linetype = "solid", size = 0.8) +
  geom_line(aes(x = Date, y = SVENY20, color = "SVENY20"), linetype = "solid", size = 0.8) +
  geom_line(aes(x = Date, y = SVENY07, color = "SVENY07"), linetype = "solid", size = 0.8) +
  geom_line(aes(x = Date, y = SVENY30, color = "SVENY30"), linetype = "solid", size = 0.8) +
  labs(
    x = "Date",
    y = "Bond Yield",
    title = "Bond Yield Comparison After COVID",
    color = "Series",
    linetype = "Series"
  ) +
  scale_color_manual(
    values = c("#0072B2", "#D55E00", "#009E73", "#FC79B2"),
    labels = c("SVENY01", "SVENY20", "SVENY07", "SVENY30")
  ) +
  scale_linetype_manual(
    values = c("solid", "solid", "solid", "solid"),
    labels = c("SVENY01", "SVENY20", "SVENY07", "SVENY30")
  ) +
  theme_minimal() +
  guides(
    color = guide_legend(override.aes = list(linetype = "solid")),
    linetype = guide_legend()
  )

```

Post Recovery the SVENY01 value went up.


## Moelling


Let's Model the first difference of the series


```{r, warning=FALSE}
df %>%
  autoplot(SVENY01 %>% difference(1))
```


```{r, warning=FALSE}
df %>%
  autoplot(SVENY01 %>% difference(7))
```
```{r, warning=FALSE}
df %>%
  autoplot(SVENY01 %>% difference(20))
```

The series is stationary but challenge here is to predict the volatility, as it is important aspect in the financial markets.

Therefore we use GARCH model.


```{r warning=FALSE}
library(cowplot)
library(forecast)

plot1 <- df %>%
  autoplot(SVENY01 %>% difference(1))+
  labs(x = "Time", y = "1 Year")

plot2 <- df %>%
  autoplot(SVENY07 %>% difference(1))+
  labs(x = "Time", y = "7 Year")


plot3 <- df %>%
  autoplot(SVENY20 %>% difference(1)) +
  labs(x = "Time", y = "20 Year")

plot_grid(plot1, plot2, plot3, ncol = 1, labels = c("A", "B", "C"))

```
The returns for 1 year has the lowest variance and 7 year return has most variance.


## Modelling - GARCH

```{r}
library(rugarch)
```


```{r}
pacf(diff(df_filled$SVENY01) , lag.max = 20) 
```


```{r}
pacf(diff(df_filled$SVENY07), lag.max = 20) 
```

Based on the above plot lets try GARCH



### SVENY01


```{r}
train_data <- df %>% 
  filter(Date < '2022-01-01') 
```

```{r}
test_data <- df %>% 
  filter(Date > '2022-01-01')
```

#### Fitting Model

```{r}
spec <- ugarchspec(distribution.model = "sstd")
fit <- ugarchfit(na.omit(diff(train_data$SVENY01)), spec = spec)
volalality <- sigma(fit)
```


#### Training Forecast

```{r, warning=FALSE}

p1 <- ggplot() +
  geom_line(aes(x = seq_along(volalality), y = volalality), color = "blue") +
  labs(x = "Time", y = "Volatility")


p2 <- train_data %>%
  mutate(difference = c(NA, diff(SVENY01))) %>%
  ggplot() +
  geom_line(aes(x = seq_along(difference), y = difference), color = "orange") +
  labs(x = "Time", y = "1 Year")


combined_plot <- cowplot::plot_grid(p1, p2, nrow = 2)


print(combined_plot)

```

```{r}
dim(test_data)
```

**The Blue line shows the volatality and orange one is the original differenced series correctly identify high varinace with a high value** 

#### Test Forecast

```{r}
predictions <- ugarchforecast(fit, n.ahead = 321)

test_volatality <- sigma(predictions)
```



```{r}
p1 <- ggplot() +
  geom_line(aes(x = seq_along(test_volatality), y = test_volatality), color = "blue") +
  labs(x = "Time", y = "Volatility")


p2 <- test_data %>%
  mutate(difference = c(NA, diff(SVENY07))) %>%
  ggplot() +
  geom_line(aes(x = seq_along(difference), y = difference), color = "orange") +
  labs(x = "Time", y = "1 Year")


combined_plot <- cowplot::plot_grid(p1, p2, nrow = 2)


print(combined_plot)
```

**In this plot the variace is shown be increasing throught time however it is not so much of the case, that because we are predicting way into the future** 

### SVENY07


#### Fitting Model

```{r}
spec <- ugarchspec(distribution.model = "sstd")
fit <- ugarchfit(na.omit(diff(train_data$SVENY01)), spec = spec)
volalality <- sigma(fit)
```

#### Training Forecast

```{r, warning=FALSE}

p1 <- ggplot() +
  geom_line(aes(x = seq_along(volalality), y = volalality), color = "blue") +
  labs(x = "Time", y = "Volatility")


p2 <- train_data %>%
  mutate(difference = c(NA, diff(SVENY07))) %>%
  ggplot() +
  geom_line(aes(x = seq_along(difference), y = difference), color = "orange") +
  labs(x = "Time", y = "7 Year")


combined_plot <- cowplot::plot_grid(p1, p2, nrow = 2)


print(combined_plot)

```

```{r}
dim(test_data)
```

**The Blue line shows the volatality and orange one is the original differenced series correctly identify high varinace with a high value** 


#### Test Forecast

```{r}
predictions <- ugarchforecast(fit, n.ahead = 321)

test_volatality <- sigma(predictions)
```



```{r}
p1 <- ggplot() +
  geom_line(aes(x = seq_along(test_volatality), y = test_volatality), color = "blue") +
  labs(x = "Time", y = "Volatility")


p2 <- test_data %>%
  mutate(difference = c(NA, diff(SVENY01))) %>%
  ggplot() +
  geom_line(aes(x = seq_along(difference), y = difference), color = "orange") +
  labs(x = "Time", y = "7 Year")


combined_plot <- cowplot::plot_grid(p1, p2, nrow = 2)


print(combined_plot)
```

**Simialar to the above test plot for SEVNY01**

### SVENY20

```{r}
train_data <- df %>% 
  filter(Date < '2022-01-01' & Date > '2000-01-01') 
```

```{r}
test_data <- df %>% 
  filter(Date > '2022-01-01')
```

#### Fitting Model

```{r}
spec <- ugarchspec(distribution.model = "sstd")
fit <- ugarchfit(na.omit(diff(train_data$SVENY20)), spec = spec)
volalality <- sigma(fit)
```

#### Training Forecast

```{r, warning=FALSE}

p1 <- ggplot() +
  geom_line(aes(x = seq_along(volalality), y = volalality), color = "blue") +
  labs(x = "Time", y = "Volatility")


p2 <- train_data %>%
  mutate(difference = c(NA, diff(SVENY20))) %>%
  ggplot() +
  geom_line(aes(x = seq_along(difference), y = difference), color = "orange") +
  labs(x = "Time", y = "7 Year")


combined_plot <- cowplot::plot_grid(p1, p2, nrow = 2)


print(combined_plot)

```

**The blue train curve is going good following the orange series**

```{r}
dim(test_data)
```



#### Test Forecast

```{r}
predictions <- ugarchforecast(fit, n.ahead = 321)

test_volatality <- sigma(predictions)
```



```{r}
p1 <- ggplot() +
  geom_line(aes(x = seq_along(test_volatality), y = test_volatality), color = "blue") +
  labs(x = "Time", y = "Volatility")


p2 <- test_data %>%
  mutate(difference = c(NA, diff(SVENY20))) %>%
  ggplot() +
  geom_line(aes(x = seq_along(difference), y = difference), color = "orange") +
  labs(x = "Time", y = "7 Year")


combined_plot <- cowplot::plot_grid(p1, p2, nrow = 2)


print(combined_plot)
```

**In this plot the variace is shown be increasing throught time and plateaus after 200 points however it is not so much of the case, that because we are predicting way into the future** 


## Rolling Forecast

Let's use a rolling forecast method where we predict some 10 days into the future as in real world we dont expect to know forecast for years.

```{r}
series <- train_data$SVENY01


```


```{r}
rolling_predictions <- c()
for (i in seq(1, nrow(test_data), 10)) {
  train <- series[1:(length(series) - (nrow(test_data) - i)) ]
  fit <- ugarchfit(train, spec = spec)
  volalality <- sigma(fit)
  predictions <- ugarchforecast(fit, n.ahead = 10)
  test_volatality <- sigma(predictions)
  rolling_predictions <- c(rolling_predictions, test_volatality)
}
```


```{r}
p1 <- ggplot() +
  geom_line(aes(x = seq_along(rolling_predictions), y = rolling_predictions), color = "blue") +
  labs(x = "Time", y = "Volatility")


p2 <- test_data %>%
  mutate(difference = c(NA, diff(SVENY20))) %>%
  ggplot() +
  geom_line(aes(x = seq_along(difference), y = difference), color = "orange") +
  labs(x = "Time", y = "7 Year")


combined_plot <- cowplot::plot_grid(p1, p2, nrow = 2)


print(combined_plot)
```
**This gives a way better forecast as we see.**


Now we try it with 5 days 
